Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-06 Documents/M1/realizableFermionicM1/sections/realizability.tex
Modified the caption of the realizable set diagram

Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in $|\vect{\cH}| - \cJ$ coordinates (light blue region).
To make this plot, a total of $10^{6}$ distribution functions of the form $\mathfrak{f}(\mu;a,b) = \dfrac{1}{e^{a+b\mu}+1}$ ($\mu\in[-1,1]$) were generated, where the parameters $a$ and $b$ were chosen randomly and independently in the range $a,b\in[-10^{2},10^{2}]$.  
A uniform $\mu$-grid with $\Delta\mu=1/128$ was used to represent the distribution functions. And the angular moments were calculated using the trapezoid rule.  
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
  \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
  Each of the $10^{6}$ light-blue points in the figure represents a set of moments $\vect{\cM}=(\cJ,\vect{\cH})$, computed from a random Fermi-Dirac distribution (see text for details).  
  Black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$.}
  \label{fig:RealizableSetFermionic}
\end{figure}

>>>>

Figure~\ref{fig:RealizableSetFermionic} illustrates the geometry of the convex set $\cR$ in $|\vect{\cH}| - \cJ$ coordinates (light blue region).

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/RealizableSetFermionic}
  \caption{Illustration of the realizable set $\cR$ defined in Eq.~\eqref{eq:realizableSet}.  
  The black lines define the boundary of $\cR$: $\gamma(\vect{\cM}) = 0$ while the dash red lines is the boundary given by the Maxwell's distributions.}
  \label{fig:RealizableSetFermionic}
\end{figure}
